Characterizing Signal Loss in the 21\,cm Reionization Power Spectrum: \\A Revised Study of PAPER-64

### 2018-08-29 PAPER.tex
read-through edits up until section 3

\begin{abstract}
The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
EoR by tracing the 21\,cm line of neutral hydrogen. Because this signal is very faint and difficult to isolate, it is crucial to develop analysis techniques that maximize sensitivity and suppress contaminants in data. It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates. Specifically, with a new generation of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal. In this paper, we focus on signal loss specifically associated with quadratic estimators and power spectrum estimation. We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of signal loss have led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64. Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for. While we only focus on a subset of PAPER-64 data in this paper, revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al. (\textit{in prep.}) and supersede results from previously published PAPER analyses.
\end{abstract}

@@

In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using 
the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).

The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often chosen to maximize sensitivity and minimize contaminants, affect power spectrum results. More specifically, it is imperative to develop techniques that ensure 
the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss may have resulted. In this paper, we discuss signal loss associated with specifically with power spectrum estimation --- a topic that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has been underestimated in previous PAPER analyses. We first approach this topic from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER. In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a related paper, Kolopanis et al. (\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.

@@

Signal loss refers to attenuation of the target \textit{cosmological} signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.

Signal loss can arise in a variety of ways in an analysis pipeline, such as by fitting a polynomial during spectral calibration, applying a delay domain filter, or deriving weights from data and applying them to itself. Here we focus on signal loss associated with 
% JEA - we're not considering a general problem, but are really just focused on the empirical QE and its discontents, so let's say that
the latter.

A dataset can be weighted to emphasize certain features and minimize others, and one particular flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}). Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes. However, a challenge of inverse covariance 
weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss. Here we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
This loss was significantly 
%applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
underestimated in the \citetalias{ali_et_al2015} analysis.

@@

%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator 
%which may still produce an unbiased estimate, 
where Equation \eqref{eq:OQEQuadratic} is replaced by
\begin{equation}
\label{eq:qhat}
\widehat{q}^{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
\end{equation}
where $\textbf{R}$ is a weighting matrix chosen by the data analyst.  For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
The matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum parameters $\partial \C/\partial P^\alpha$ but in practice also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jy to Kelvin.
%with dimensions ($N_{f}$,$N_{f}$) --- as

%%% COME BACK HERE
% Need to still explain the motivation for this
With an appropriate normalization matrix $\textbf{M}$, the quantity
%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
\begin{equation}
\label{eq:phat}
\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
\end{equation}
is a sensible estimate of the true power spectrum $\textbf{P}$. To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
\begin{eqnarray}
\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
&\equiv & \sum_{\beta} W^{\alpha \beta} P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
\end{eqnarray}
where $W^{\alpha \beta}$ are elements of a window function matrix. Let's consider the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit). If $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias. However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate. In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized. Beyond this, the data analyst has a choice for $
\textbf{M}$, and for simplicity throughout this paper we choose $\textbf{M}$ to be diagonal. In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated. If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
% JEA - is one really free to choose M and R independently?

% JEA - I don't think it's attractive at all
%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. 
Given the advantages of inverse covariance weighting, a question arises of how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}. In previous PAPER analyses, one time-averages the data to obtain:
\begin{equation}
\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t} \approx \langle  \textbf{xx}^{\dagger}\rangle,
\end{equation}
assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to $0$ over a sufficient 
amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$, where we use a hat symbol to distinguish the empirical covariance from the true covariance $\textbf{C}$.

@@

\item The rate at which empirical eigenvectors converge to their true forms depends on sample variance in the empirical estimate and the steepness (the degeneracy) of the empirical eigenspectrum. In general, larger sample variances and flatter eigenspectra (more degeneracies) lead to more loss (Section \ref{sec:toymodel_frf}).

@@

\subsection{Inverse Covariance Weighting}
\label{sec:toymodel}

@@

For the case of a mode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.  However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data. If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}. As shown mathematically in Appendix \ref{sec:sigloss_appendix}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.  In short, {\it if the covariance is computed from the data itself, it carries the risk of over-fitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}

@@

Armed with this information,
%Using what we've learned about the eigenspectrum, 
we can tweak the covariance in a simple way to suppress foregrounds and yield minimal signal loss. Recall that our toy model foreground 
% JEA - modes need not be sinusoids; the point is that there is one outer product describing this in the covariance
%is a sinusoid, so it 
can be perfectly described by a single eigenmode. Using the full dataset's (foreground plus EoR signal) empirical covariance, we can 
project out the zeroth eigenmode and 
%then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes. Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of over-fitting that can happen for those modes (i.e., only allowing over-fitting to occur for the first mode).
then take the remaining covariance to be the identity matrix.  
This decouples the covariance from the data for the EoR modes.  The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. 
In this case we recover the EoR signal, demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can suppress
% down-weight them 
foregrounds with negligible signal loss.

Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that changes its coupling to the data realization. There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.

@@

A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}). Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes which are noise-like.

@@

While the connection between the rate of convergence of an empirical eigenvector with the steepness of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss. The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged, there will not be any signal loss. However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.

@@

With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our original toy model used in Section \ref{sec:toymodel}, which is comprised of a mock foreground and mock EoR signal. We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}). We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will still be full rank. We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}

@@

As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be 
avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e., the identity), instead of computing it based on $\textbf{x}
_{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}_{\rm reg}$ (regularized empirical covariance matrix) to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
left), we see that there is negligible signal loss. This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid over-fitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations). 
%This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we do not know how to separate out the foregrounds from the EoR in our data.

@@

Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the ``foreground-quiet" range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to 
down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time. Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from 
data that is similar but not exactly the same as the data that is being down-weighted. Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from over-fitting EoR modes in the power spectrum dataset itself.

>>>>

\begin{abstract}
The Epoch of Reionization (EoR) is an uncharted era in our Universe's history during which the first stars and 
galaxies led to the ionization of neutral hydrogen in the intergalactic medium. There are many experiments investigating the 
EoR by tracing the 21\,cm line of neutral hydrogen. Because this signal is very faint and difficult to isolate, it is crucial to develop analysis techniques that maximize sensitivity and suppress contaminants in data. It is also imperative to understand the trade-offs between different analysis methods and their effects on power spectrum estimates. Specifically, with a new generation of instruments and a statistical power spectrum detection in our foreseeable future, it has become increasingly important to understand how certain analysis choices can lead to the loss of the EoR signal. In this paper, we focus on signal loss associated with power spectrum estimation. We describe the origin of this loss using both toy models and data taken by the 64-element configuration of the Donald C. Backer Precision Array for Probing the Epoch of Reionization (PAPER). In particular, we highlight how detailed investigations of signal loss have led to a revised, higher 21\,cm power spectrum upper limit from PAPER-64. Additionally, we summarize errors associated with power spectrum error estimation that were previously unaccounted for. While we only focus on a subset of PAPER-64 data in this paper, revised power spectrum limits from the PAPER experiment are presented in a forthcoming paper by Kolopanis et al. (\textit{in prep.}) and supersede results from previously published PAPER analyses.
\end{abstract}

@@

In addition to the first tentative detection of our \textit{Cosmic Dawn} (pre-reionization era) made by the Experiment to Detect the Global EoR Signature (EDGES; \citealt{bowman_et_al2018}; \citealt{bowman2010}), there are several radio telescope experiments that have succeeded in using 
the 21\,cm signal from hydrogen to place constraints on the brightness of the signal. Examples of experiments investigating the 
mean brightness temperature of the 21\,cm signal relative to the CMB are the Large Aperture Experiment to Detect the Dark Ages (LEDA; \citealt{bernardi_et_al2016}), the 
Dark Ages Radio Explorer (DARE; \citealt{burns2012}), the Sonda Cosmol\'ogica de las Islas para la Detecci\'on de 
Hidr\'ogeno NeutroSciHi (SCI-HI; \citealt{voytek2014}), the Broadband Instrument for Global HydrOgen ReioNisation Signal 
(BIGHORNS; \citealt{sokolowski2015}), and the Shaped Antenna measurement of the background RAdio Spectrum (SARAS; 
\citealt{patra2015}). Radio interferometers which seek to measure statistical power spectra include the Giant Metre-wave 
Radio Telescope (GMRT; \citealt{paciga_et_al2013}), the LOw Frequency ARray (LOFAR; \citealt{van_haarlem_et_al2013}), 
the Murchison Widefield Array (MWA; \citealt{tingay_et_al2013}), the 21 Centimeter Array (21CMA; 
\citealt{peterson_et_al2004}; \citealt{wu2009}), the Square Kilometre Array (SKA; \citealt{koopmans_et_al2015}), and PAPER (\citealt{parsons_et_al2010}). The Hydrogen Epoch of 
Reionization Array (HERA), which is currently being built, is a next-generation instrument that aims to combine lessons 
learned from previous experiments and has a forecasted sensitivity capable of a high-significance power spectrum 
detection with an eventual $350$ elements using current analysis techniques (\citealt{pober_et_al2014}; \citealt{liu_parsons_2016}; \citealt{dillon_parsons2016}; \citealt{deboer_et_al2017}).

The major challenge that faces all 21\,cm experiments is isolating a small signal that is buried underneath foregrounds and 
instrumental systematics that are, when combined, four to five orders of magnitude brighter \citep[e.g.,][]{santos_et_al2005, ali_et_al2008, deOliveiraCosta_et_al2008, jelic_et_al2008, bernardi_et_al2009, bernardi_et_al2010, ghosh_et_al2011, pober_et_al2013b, bernardi_et_al2013, dillon_et_al2014, kohn_et_al2016}. A clean measurement therefore requires an intimate understanding of how data analysis choices, which are often tailored to maximize sensitivity and minimize contaminants, affect power spectrum results. More specifically, it is imperative to develop techniques that ensure 
the accurate extraction and recovery of the EoR signal, despite the analysis method chosen and how much loss (of both contaminants and the EoR signal) accompanies the method. In this paper, we specifically discuss signal loss --- the loss of the \textit{cosmological} signal --- associated with power spectrum estimation. This is an issue that is essential to investigate for a robust 21\,cm power spectrum analysis and one that has motivated a revised PAPER analysis. We first approach this topic from a broad perspective, and then perform a detailed 
case study using data from the 64-element configuration of PAPER. In this study we use a subset of PAPER-64 data to illustrate our revised analysis methods, while a related paper, Kolopanis et al. (\textit{in prep.}), builds off of the methods in this paper to present revised PAPER-64 results for multiple redshifts and baseline types.

@@

Signal loss refers to attenuation of the target cosmological signal 
in a power spectrum estimate. Certain analysis techniques can cause this loss, and if the amount of loss is not quantified accurately, it could lead to false non-detections and overly aggressive upper limits. Determining whether an analysis pipeline is lossy, and estimating the amount of loss if so, has subtle challenges but is necessary to ensure the accuracy of any result.

One type of signal loss can occur when weighting data by itself. Broadly speaking, a dataset can be weighted to emphasize certain features and minimize others. For example, one flavor of weighting employed by previous PAPER analyses is inverse covariance weighting in frequency, which is a generalized version of inverse variance weighting that also takes into account frequency correlations (\citealt{liu_tegmark2011}; \citealt{dillon_et_al2013a}; \citealt{liu_et_al2014a}; \citealt{liu_et_al2014b}; \citealt{dillon_et_al2014}; \citealt{dillon_et_al2015}). Using such a technique enables the down-weighting of contaminant modes that obey a different covariance structure from that of cosmological modes. However, a challenge of inverse covariance 
weighting is in estimating a covariance matrix that is closest to the true covariance of the data; the discrepancy between the two, as we will see, can have large impacts on signal loss. In this paper we focus specifically on loss associated with the use of an empirically estimated covariance matrix with the ``optimal quadratic estimator'' formalism.
This loss was significantly 
%applying a weighting matrix to data, a loss that can be significant depending on the choice of weighting and one that was previously 
underestimated in the \citetalias{ali_et_al2015} analysis and is the main reason motivating a revised power spectrum result.

@@

%We do this when forming the un-normalized power spectrum estimate $\widehat{q}_{\alpha}$:
Motivated by the desire to retain the advantageous behavior of suppressing contributions of $\mathbf{U}$ to estimates of the EoR power spectrum, we note that is possible to define a modified version of the quadratic estimator 
%which may still produce an unbiased estimate, 
where Equation \eqref{eq:OQEQuadratic} is replaced by
\begin{equation}
\label{eq:qhat}
\widehat{q}^{\alpha} = \frac{1}{2}\textbf{x}^{\dagger}\textbf{R}\textbf{Q}^{\alpha}\textbf{R}\textbf{x}
\end{equation}
where $\textbf{R}$ is a weighting matrix chosen by the data analyst.  For example, inverse covariance weighting (the optimal form of QE) would set $\textbf{R} \equiv \textbf{C}^{-1}$ and a uniform-weighted case would use $\textbf{R} \equiv \textbf{I}$, the identity matrix.
Again, the matrix $\textbf{Q}^{\alpha}$ encodes the dependence of the covariance on the power spectrum but in practice also also does other things, including implementing a transform of the frequency domain visibilities to $\mathbf{k}$-space, taking into account cosmological scalings, and converting the visibilities from Jansky to Kelvin.
%with dimensions ($N_{f}$,$N_{f}$) --- as

%%% COME BACK HERE
% Need to still explain the motivation for this
With an appropriate normalization matrix $\textbf{M}$, the quantity
%We normalize our power spectrum estimates using the matrix $\textbf{M}$:
\begin{equation}
\label{eq:phat}
\widehat{\textbf{P}} = \textbf{M}\widehat{\textbf{q}}
\end{equation}
is a sensible \textit{estimate} of the \textit{true} power spectrum $\textbf{P}$.

To ensure that $\textbf{M}$ correctly normalizes our power spectrum, one may take the expectation value of Equation \eqref{eq:phat} to obtain
\begin{eqnarray}
\langle \widehat{P}^\alpha \rangle &=& \frac{1}{2} \sum_{\beta \gamma} M^{\alpha \gamma}  \textrm{tr} \left( \textbf{R}\textbf{Q}^{\gamma}\textbf{R} \textbf{Q}^{\beta}\right) P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right) \nonumber \\
&\equiv & \sum_{\beta} W^{\alpha \beta} P^\beta +\frac{1}{2} \sum_{ \gamma}  \Tr\left( \mathbf{U} \textbf{R} \textbf{Q}^{\gamma} \mathbf{R} \right), \label{eq:Wpplusbias}
\end{eqnarray}
where $W^{\alpha \beta}$ are elements of a window function matrix. Considering the first term of this expression (again, we are assuming that the linear bias term is significantly suppressed; and if this is not the case, we are simply assuming that we are setting a conservative upper limit), if $\mathbf{W}$ ends up being the identity matrix for our choices of $\mathbf{R}$ and $\mathbf{M}$, then we recover Equation \eqref{eq:super_unbiased} for the first term, and we have an estimator that has no multiplicative matrix bias. However, Equation \eqref{eq:super_unbiased} is a rather restrictive condition, and it is possible to violate it and still have a sensible (and correctly normalized) power spectrum estimate. In particular, as long as the rows of $\mathbf{W}$ sum to unity, our power spectrum will be correctly normalized. Beyond this, the data analyst has a choice for $
\textbf{M}$, and for simplicity throughout this paper we choose $\textbf{M}$ to be diagonal. In a preview of what is to come, we also stress that the derivation that leads to Equation \eqref{eq:Wpplusbias} assumes that $\mathbf{R}$ and $\mathbf{x}$ are not correlated. If this assumption is violated, a simple application of the (now incorrect) formulae in this section can result in an improperly normalized power spectrum estimator that does not conserve power, i.e., one that has signal loss.
% JEA - is one really free to choose M and R independently?

% JEA - I don't think it's attractive at all
%Without a perfect model for the covariance matrix $\textbf{C}$ of our data, one attractive way to estimate it is to empirically derive it from the data $\textbf{x}$ itself. 
Given the advantages of inverse covariance weighting, a question arises of how one goes about estimating $\C$.  One method is to empirically derive it from the data $\textbf{x}$ itself.
Similar types of weightings that are based on variance information in data are done in \citet{chang_et_al2010} and \citet{switzer_et_al2015}. In previous PAPER analyses, one time-averages the data to obtain:
\begin{equation}
\widehat{\textbf{C}} \equiv \langle\textbf{xx}^{\dagger}\rangle_{t} \approx \langle  \textbf{xx}^{\dagger}\rangle,
\end{equation}
assuming $\langle\textbf{x}\rangle_{t} = 0$ (a reasonable assumption since fringes average to zero over a sufficient 
amount of time), where $\langle \rangle_{t}$ denotes a finite average over time. The weighting matrix for our empirically estimated inverse covariance weighting is then $
\textbf{R} \equiv \widehat{\textbf{C}}^{-1}$, where we use a hat symbol to distinguish the empirical covariance from the true covariance $\textbf{C}$.

@@

\item The rate at which empirical eigenvectors converge to their true forms depends on the sample variance in the empirical estimate and the shape of the empirical eigenspectrum. In general, larger sample variances lead to more loss (Section \ref{sec:toymodel_frf}).

@@

\subsection{Empirical Inverse Covariance Weighting}
\label{sec:toymodel}

@@

For the case of an eigenmode which can be safely assumed to be predominantly a foreground, its presence in the true covariance matrix will result in the desired suppression via a kind of projection (Equations \ref{eq:IdealToyModelCovariance} and \ref{eq:IdealToyModelEstimator}); whether or not it is strongly correlated with the the actual data vector is irrelevant.  However, in the case of an empirically estimated covariance matrix, the eigenmodes of $\widehat{\textbf{C}}_{\rm EoR}$ will both be incorrect and can be correlated with the data. If these incorrect eigenmodes are not correlated with the data, it will lead to non-minimum variance estimates but will not produce the suppression of the power spectrum amplitude as seen in the left plot of Figure \ref{fig:toy_sigloss3}. As described in Section \ref{sec:siglossmethod} and shown mathematically in Appendix \ref{sec:sigloss_appendix}, however, if $\widehat{\mathbf{C}}_{\rm EoR}$ $\textit{is}$ correlated with the data vector $\mathbf{x}$, there is a kind of projection of power in the {\it non}-foreground modes from the resulting power spectrum estimate, thus producing an estimate that is biased low.  In short, {\it if the covariance is computed from the data itself, it carries the risk of overfitting information in the data and introducing a multiplicative bias (per $k$) to estimates of the signal.}

@@

Armed with this information,
%Using what we've learned about the eigenspectrum, 
we can tweak the covariance in a simple way to suppress foregrounds and yield minimal signal loss. Recall that our toy model foreground 
% JEA - modes need not be sinusoids; the point is that there is one outer product describing this in the covariance
%is a sinusoid, so it 
can be perfectly described by a single eigenmode. Using the full dataset's (foreground plus EoR signal) empirical covariance, we can 
project out the zeroth eigenmode and 
%then flatten the rest of the spectrum to have eigenvalues of 1, thereby down-weighting the foreground-dominated mode more than the rest of the modes. Hence, we are changing the EoR-dominating part of the spectrum to be less coupled to the data, limiting the amount of overfitting that can happen for those modes (i.e., only allowing overfitting to occur for the first mode).
then take the remaining covariance to be the identity matrix.  
This decouples the covariance from the data for the EoR modes.  The resulting power spectrum estimate for this case is shown in the right plot of Figure \ref{fig:toy_sigloss3}. 
In this case we recover the EoR signal, demonstrating that if we can disentangle the foreground-dominated modes and EoR-dominated modes, we can suppress
% down-weight them 
foregrounds with negligible signal loss.

Altering $\widehat{\textbf{C}}$ as such is one specific example of a regularization method for this toy model, in which we are changing $\widehat{\textbf{C}}$ in a way that reduces its coupling to the data realization. There are several other simple ways to regularize $\widehat{\textbf{C}}$, and we will discuss some in Section 
\ref{sec:otherweight}.

@@

A fringe-rate filter is an analysis technique designed to maximize sensitivity by integrating in time (\citealt{parsons_et_al2016}). Rather than a traditional box-car average in time, a time domain filter can be designed to up-weight temporal modes consistent with the sidereal motion on the sky, while down-weighting modes that are noise-like.

@@

While the connection between the rate of convergence of an empirical eigenvector with the sample variance of an eigenspectrum is interesting, it is also important to note that regardless of convergence rate, any mode that is coupled to the data is susceptible to signal loss. The true eigenvectors are not correlated with the data realizations; thus, if our empirical eigenvectors are converged fully, there will not be any signal loss. However, an unconverged eigenvector estimate will retain some memory of the data realizations used in its generation, leading to signal loss.

@@

With Figures \ref{fig:toy_sigloss16} and \ref{fig:toy_sigloss17} establishing the connection between convergence rates (of empirical covariances and eigenvectors) and number of realizations, we now turn back to our original toy model used in Section \ref{sec:toymodel}, which is comprised of a mock foreground and mock EoR signal. We mimic a fringe-rate filter by averaging every four time integrations of our toy model dataset together, yielding $25$ independent samples in time (Figure \ref{fig:toy_sigloss5}). We choose these numbers so that the total number of independent samples is similar to the number of frequency channels --- hence our matrices will be full rank. We use this ``fringe-rate filtered" mock data for the remainder of Section \ref{sec:SiglossOverview}.
%\footnote{If instead we average every $20$ samples together, yielding only $5$ independent samples in time, we are left with a rank deficient covariance matrix. In this case... \cc{fill in}}

@@

As a first test, we model the covariance matrix of EoR as a proof of concept that if perfect models are known, signal loss can be 
avoided. We know that our simulated EoR signal should have a covariance matrix that mimics the identity matrix, with its 
variance encoded along the diagonal. We model $\textbf{C}_{\rm EoR}$ as such (i.e., the identity), instead of computing it based on $\textbf{x}
_{\rm EoR}$ itself. Next, we add $\textbf{C}_{\rm EoR} + \widehat{\textbf{C}}_{\rm FG}$ (where $\widehat{\textbf{C}}_{\rm FG} = \langle\textbf{x}_{\rm FG}
\textbf{x}_{\rm FG}^{\dagger}\rangle_{t}$) to obtain a final $\widehat{\textbf{C}}_{\rm reg}$ (regularized empirical covariance matrix) to use in weighting. In Figure \ref{fig:toy_sigloss8} (upper 
left), we see that there is negligible signal loss. This is because by modeling $\textbf{C}_{\rm EoR}$, we avoid overfitting EoR fluctuations in the data that our model doesn't know about (but, an empirically derived $\widehat{\textbf{C}}_{\rm EoR}$ would know about the fluctuations). 
%This is also shown by comparing the (steeper) green and (flatter) red curves in Figure \ref{fig:toy_sigloss14}. 
In practice such a weighting option is not feasible, as it is difficult to model $\textbf{C}_{\rm EoR}$, and $\widehat{\textbf{C}}_{\rm FG}$ is unknown because we do not know how to separate out the foregrounds from the EoR in our data.

@@

Another possible way to regularize $\widehat{\textbf{C}}$ is to use information from different ranges of LST. For example, one could 
calculate $\widehat{\textbf{C}}$ with data from LSTs where foregrounds are stronger (earlier or later LSTs than the ``foreground-quiet" range typically used in forming power spectra) --- doing so may yield a better description of the foregrounds that we desire to 
down-weight, especially if residual foreground chromaticity is instrumental in origin and stable in time. Fundamentally, each of these examples are similar in that they rely on a computation of $\widehat{\textbf{C}}$ from 
data that is similar but not exactly the same as the data that is being down-weighted. Ideally this would be effective in down-weighting shared contaminants yet avoid signal loss from overfitting EoR modes in the power spectrum dataset itself.
